Supporting Information:\\ Headgroup structure and cation binding in phosphatidylserine lipid bilayers

### 2019-05-29 Manuscript/manuscriptPSsuppl.tex
Update manuscriptPSsuppl.tex

\noindent
{\it POPS bilayers with Na$^+$ counterions.}
%The data in Table \ref{PSsystems} and Refs \citenum{macrogPOPS298Kcorrect,macrogPOPS298KwithK}
%\todo{T. Piggot and M. Javanainen, please write simulation details} \\
%\hl{Piggot: please write about system with Na$^+$ counterions}.
Force field parameters for POPS simulations with the MacRog OPLS-AA force field~\cite{maciejewski14,kulig15b,rog16}
were constructed manually using the provided PS parameters as a guide~\cite{rog16}. The original parameters were
not used due to an incorrect arrangement of the {\it sn}-1 and {\it sn}-2 tails (i.e. the lipid was OPPS and not POPS).
The corrected parameters are available from Ref.~\citenum{macrogPOPS298KwithK}.
The starting structure was the same as that used in the CHARMM36 POPS simulations (with Na$^+$ ions) and was converted into
the correct format using a script to adjust the atom order. Water was treated using the TIP3P model~\cite{jorgensen83}.
Simulation parameters were chosen to closely mimic those used in the original force field publications~\cite{maciejewski14,kulig15b,rog16}:
van der Waals interactions were truncated at 1.0~nm with a dispersion correction applied to the energy and pressure;
Long-range Coulombic interactions were treated with PME beyond a system-optimized cut-off.
All other simulation settings were identical to those described above for the CHARMM36 DOPS and POPS simulations,
including use of the Verlet cut-off scheme~\cite{Pall13}, apart from the use of LINCS to constrain all bonds during these simulations.

@@

\noindent
{\it Batuhan Kav}

\noindent
{\it Jesper J. Madsen}

>>>>

\noindent
{\it POPS bilayers with Na$^+$ counterions.}
%The data in Table \ref{PSsystems} and Refs \citenum{macrogPOPS298Kcorrect,macrogPOPS298KwithK}
%\todo{T. Piggot and M. Javanainen, please write simulation details} \\
%\hl{Piggot: please write about system with Na$^+$ counterions}.
Force field parameters for POPS simulations with the MacRog OPLS-AA force field~\cite{maciejewski14,kulig15b,rog16}
were constructed manually using the provided PS parameters as a guide~\cite{rog16}. The original parameters were
not used due to an incorrect arrangement of the {\it sn}-1 and {\it sn}-2 tails (i.e. the lipid was OPPS and not POPS).
The corrected parameters are available from Ref.~\citenum{macrogPOPS298KwithK}.
The starting structure was the same as that used in the CHARMM36 POPS simulations (with Na$^+$ ions) and was converted into
the correct format using a script to adjust the atom order. Water was treated using the TIP3P model~\cite{jorgensen83}.
Simulation parameters were chosen to closely mimic those used in the original force field publications~\cite{maciejewski14,kulig15b,rog16}:
van der Waals interactions were truncated at 1.0~nm with a dispersion correction applied to the energy and pressure;
Long-range Coulombic interactions were treated with PME beyond a system-optimized cut-off.
All other simulation settings were identical to those described above for the CHARMM36 DOPS and POPS simulations,
including use of the Verlet cut-off scheme~\cite{Pall13}, apart from the use of LINCS to constrain all bonds during these simulations.
Simulations with the group cut-off scheme gave slightly lower area per molecule ($\sim$~50\AA$^2$) than
the simulations with Verlet cut-off ($\sim$~52\AA$^2$).

@@

\noindent
{\it Batuhan Kav}
Set up, performed, and analyzed Amber Lipid14/17 simulations with the Amber MD. 
\noindent
{\it Jesper J. Madsen}
Set up, performed and analyzed several of the CHARMM36 simulations. Provided comments on the manuscript.
